Estimating Real-Time Highstreet Footfall from Wi-Fi Probe Requests

### 2019-02-21 paper/sections/main_study.tex
final submission

\begin{figure}
	\begin{center}
		\includegraphics [width=0.90\linewidth] {images/main_schedule.jpeg}
		\caption{Data collection schedule showing the days when sensors were active at their corresponding locations. The red squares show that manual counting of pedestrians was also done on that day.}
		\label{main_schedule}
	\end{center}
\end{figure}

@@

\begin{figure}
	\centering
	\subfigure[Installation configuration of sensors at the survey locations (not to scale)]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 20 6,clip]{images/main_configs.jpeg}}}\hspace{20pt}
	\subfigure[Density distribution of signal strength reported in collected probe requests (lower values show higher signal strength)]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 4 25 6,clip]{images/main_signals.jpeg}}}
	\caption{Distribution of signal strengths across locations} \label{main_signal_strength}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\includegraphics [width=\linewidth,trim=6 6 6 6,clip] {images/main_comparison.jpeg}
		\caption{Comparison of the filtering process with the ground truth in all the locations.}
		\label{main_comparison}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics [width=\linewidth] {images/main_footfall.jpeg}
		\caption{A week of pedestrian footfall at the Strand, London collected by the methodology. The counts are aggregated for 5 minute intervals.}
		\label{main_study_counts}
	\end{center}
\end{figure}

>>>>

\begin{figure}
	\begin{center}
		\includegraphics [width=0.90\linewidth] {images/figure_5.jpeg}
		\caption{Data collection schedule showing the days when sensors were active at their corresponding locations. The red squares show that manual counting of pedestrians was also done on that day.}
		\label{main_schedule}
	\end{center}
\end{figure}

@@

\begin{figure}
	\centering
	\subfigure[Installation configuration of sensors at the survey locations (not to scale)]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 20 6,clip]{images/figure_6a.jpeg}}}\hspace{20pt}
	\subfigure[Density distribution of signal strength reported in collected probe requests (lower values show higher signal strength)]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 4 25 6,clip]{images/figure_6b.jpeg}}}
	\caption{Distribution of signal strengths across locations} \label{main_signal_strength}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\includegraphics [width=\linewidth,trim=6 6 6 6,clip] {images/figure_7.jpeg}
		\caption{Comparison of the filtering process with the ground truth in all the locations.}
		\label{main_comparison}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics [width=\linewidth] {images/figure_8.jpeg}
		\caption{A week of pedestrian footfall at the Strand, London collected by the methodology. The counts are aggregated for 5 minute intervals.}
		\label{main_study_counts}
	\end{center}
\end{figure}

### 2019-02-21 paper/sections/methodology.tex
final submission

\begin{figure} 
	\centering \includegraphics[width=\linewidth]
		{images/datacollection_schematic.jpeg}
	\caption 
		{Schematic diagram showing the process of collecting and storing probe
		requests using the sensor}
	\label{datacollection_schematic} 
\end{figure}

@@

\begin{figure} 
\centering 
\subfigure [Distribution of signal strengths (dBm) showing the filtering of
		background noise] {\resizebox*{0.45\linewidth}{!}
		{\includegraphics{images/methodology_signalstrength.jpeg}}}
\hspace{20pt}
\subfigure [Clustering probe requests as nodes in a graph using increasing
		sequence numbers] {\resizebox*{0.45\linewidth}{!}
		{\includegraphics{images/methodology_clustering.jpeg}}}
\caption {Schematic diagrams explaining the methods for filtering by signal
	strength and clustering using sequence numbers}
\label{methodology_schematic}
\end{figure}

>>>>

\begin{figure} 
	\centering \includegraphics[width=\linewidth]
		{images/figure_1.jpeg}
	\caption 
		{Schematic diagram showing the process of collecting and storing probe
		requests using the sensor}
	\label{datacollection_schematic} 
\end{figure}

@@

\begin{figure} 
\centering 
\subfigure [Distribution of signal strengths (dBm) showing the filtering of
		background noise] {\resizebox*{0.45\linewidth}{!}
		{\includegraphics{images/figure_2a.jpeg}}}
\hspace{20pt}
\subfigure [Clustering probe requests as nodes in a graph using increasing
		sequence numbers] {\resizebox*{0.45\linewidth}{!}
		{\includegraphics{images/figure_2b.jpeg}}}
\caption {Schematic diagrams explaining the methods for filtering by signal
	strength and clustering using sequence numbers}
\label{methodology_schematic}
\end{figure}

### 2019-02-21 paper/sections/pilot_study.tex
final submission

\begin{figure}
\begin{center}
\vspace{10pt}
\includegraphics [width=0.85\linewidth,trim=10 15 10 15,clip]
    {images/pilot_clustering_params_rev.png}
\caption{The clustering process was repeated with both increasing sequence
    number threshold ($\alpha$) and time threshold ($\beta$), until we arrived
    at the lowest parameters where the know device (black line) is clustered as
    a single device.}
\label{pilot_clustering_params}
\end{center}
\end{figure}

\begin{figure}
\centering
\subfigure[Clustering probe requests based on increasing sequence numbers 
	present in them.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/pilot_clustering_rev1.jpeg}}}
\hspace{20pt}
\subfigure[Comparison of sensor based counts with the ground truth.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/pilot_comparison.jpeg}}}
\caption{The results of the pilot study demonstrating the validity of the
	methodology.} 
\label{pilot_results}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics [width=\linewidth,trim=1 1.5 1 1.5,clip]
    {images/figure_3.jpeg}
\caption{The clustering process was repeated with both increasing sequence
    number threshold ($\alpha$) and time threshold ($\beta$), until we arrived
    at the lowest parameters where the know device (black line) is clustered as
    a single device.}
\label{pilot_clustering_params}
\end{center}
\end{figure}

\begin{figure}
\centering
\subfigure[Clustering probe requests based on increasing sequence numbers 
	present in them.]
	{\resizebox*{0.475\linewidth}{!}
	{\includegraphics{images/figure_4a.jpeg}}}
\hspace{20pt}
\subfigure[Comparison of sensor based counts with the ground truth.]
	{\resizebox*{0.45\linewidth}{!}
	{\includegraphics{images/figure_4b.jpeg}}}
\caption{The results of the pilot study demonstrating the validity of the
	methodology.} 
\label{pilot_results}
\end{figure}
